Pteropod physiological analysis

### 2018-08-03 figures.Rmd
flour to chla lab, figures only

envphy <- select(dat_bio, one_of(envchr)) %>% 
  select(-Lat) %>% 
  decostand(method = 'range')
ptephy <- select(dat_bio, one_of(biochr)) %>% 
  decostand(method = 'range')

@@

envphy <- select(dat_phy, one_of(envchr)) %>% 
  select(-Lat) %>% 
  decostand(method = 'range')
ptephy <- select(dat_phy, -one_of(envchr)) %>% 
  decostand(method = 'range')

@@

```{r corplo, fig.height = 6, fig.width = 7}
levs <- c(sort(envchr), sort(biochr), sort(phychr))
labs <- c('Omega[ar]', 'Fluor', 'Lat', 'O[2]', 'pCO[2]', 'pH', 'Temp', 'CAT', 'GR', 'GSHonGSSG', 'GST', ' LPX', 'ORAC', 'ORACvLPX', 'SOD', 'abundance', 'dissolution', 'length', 'scarring', 'typeII', 'typeIII')
prplo <- crs %>% 
  separate(pr, c('cor', 'sig'), sep = ' ') %>% 
  filter(var1 %in% levs & var2 %in% levs) %>%  
  mutate(
    cor = as.numeric(cor), 
    var1 = factor(var1, levels = rev(levs), labels = rev(labs)), 
    var2 = factor(var2, levels = rev(levs), labels = rev(labs)), 
    sig = gsub('ns', '', sig)
  )

@@

p1 <- toplo$plos[[1]] + ggtitle('(b)')
p2 <- toplo$plos[[2]] + ggtitle('(a)')
p3 <- toplo$plos[[3]] + ggtitle('(c)')

>>>>

envphy <- select(dat_bio, one_of(envchr)) %>% 
  select(-Lat) %>% 
  rename(Chla = Fluor) %>% 
  decostand(method = 'range')
ptephy <- select(dat_bio, one_of(biochr)) %>% 
  decostand(method = 'range')

@@

envphy <- select(dat_phy, one_of(envchr)) %>% 
  select(-Lat) %>%
  rename(Chla = Fluor) %>% 
  decostand(method = 'range')
ptephy <- select(dat_phy, -one_of(envchr)) %>% 
  decostand(method = 'range')

@@

```{r corplo, fig.height = 6, fig.width = 7}
levs <- c(sort(envchr), sort(biochr), sort(phychr))
labs <- c('Omega[ar]', 'Chla', 'Lat', 'O[2]', 'pCO[2]', 'pH', 'Temp', 'CAT', 'GR', 'GSHonGSSG', 'GST', ' LPX', 'ORAC', 'ORACvLPX', 'SOD', 'abundance', 'dissolution', 'length', 'scarring', 'typeII', 'typeIII')
prplo <- crs %>% 
  separate(pr, c('cor', 'sig'), sep = ' ') %>% 
  filter(var1 %in% levs & var2 %in% levs) %>%  
  mutate(
    cor = as.numeric(cor), 
    var1 = factor(var1, levels = rev(levs), labels = rev(labs)), 
    var2 = factor(var2, levels = rev(levs), labels = rev(labs)), 
    sig = gsub('ns', '', sig)
  )

@@

p1 <- toplo$plos[[1]] + ggtitle('(b)') + xlab('Chla')
p2 <- toplo$plos[[2]] + ggtitle('(a)')
p3 <- toplo$plos[[3]] + ggtitle('(c)')
